Emitter Source Geolocation from Imparted Rotor Blade Modulation

### 2016-10-24 Background.tex
starting edits for figures, got to end of azimuth sim

@@

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/background/2d_theoretical_doppler_profile.eps}
		\caption{Doppler Frequency vs. Rotor Position with varying Elevation Angle}
		\label{fig:2D_theoretical_doppler}
	\end{center}
\end{figure}

@@

%formulate the geometric equations
\begin{equation}
	MaxUpperEnvelope = f_{DopplerMax}cos(\theta_{Limited})
	\label{eq:theory_90_upper}
\end{equation}

@@

\begin{equation}
	MinLowerEnvelope = -f_{DopplerMax}cos(\theta_{Limited})
	\label{eq:theory_90_lower}
\end{equation}

where $MaxUpperEnvelope$ is an array of the maximum upper envelope values for each elevation sample, $MinLowerEnvelope$ is an array of minimum lower envelope values for each elevation sample, and $\theta_{Limited}$ is the limited elevation angle range

\begin{equation}
	\theta_{Limited} = atan\left(\frac{Rx_z}{[0,\dots, (BladeLength - Rx_y)]}\right)
	\label{eq:theory_90_limited}
\end{equation}

where $Rx_z$ is the receivers position below the rotor head, $BladeLength$ is the length of the rotor blade, and $Rx_y$ is the receivers position on the Y axis.

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/background/3d_geometry_tx_90az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 90\textdegree}
		\label{fig:3D_model_90az_doppler}
	\end{center}
\end{figure}

@@

\begin{equation}
	\theta_{Limited} = atan\left(\frac{Rx_z}{[0, \dots, BladeLength]}\right)
	\label{eq:theory_270_limited}
\end{equation}

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/background/3d_geometry_tx_270az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 270\textdegree}
		\label{fig:3D_model_270az_doppler}
	\end{center}
\end{figure}

@@

%formulate the geometric equations
\begin{equation}
	MaxUpperEnvelope = f_{DopplerMax}cos(\theta_{El})
	\label{eq:theory_180_upper}
\end{equation}

and the $MinLowerEnvelope$ is set to 0 for the range.

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/background/3d_geometry_tx_180az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 180\textdegree}
		\label{fig:3D_model_180az_doppler}
	\end{center}
\end{figure}

Figure \ref{fig:3D_model_180az_doppler} shows the maximum and minimum Doppler envelope values versus elevation angle for a transmitter at an azimuth angle of 180\textdegree. The data from the figure shows the maximum, of the Doppler profile, decrease as the elevation angle gets larger.

@@

%formulate the geometric equations
\begin{equation}
	MinLowerEnvelope = -f_{DopplerMax}cos(\theta_{El})
	\label{eq:theory_0_lower}
\end{equation}

and the $MaxUpperEnvelope$ is set to 0 for the range.

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/background/3d_geometry_tx_0az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 0\textdegree}
		\label{fig:3D_model_0az_doppler}
	\end{center}
\end{figure}

Figure \ref{fig:3D_model_0az_doppler} shows the maximum and minimum Doppler envelope values versus elevation angle for a transmitter at an azimuth angle of 0\textdegree. The data from the figure shows the minimum of the Doppler profile increase as the elevation angle gets larger.

>>>>

\section{Thesis Scope}
\textcolor{red}{ADD WHAT THIS THESIS IS AND POINT OUT WHAT IT IS NOT!}

@@

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/background/2d_theoretical_doppler_profile.eps}
		\caption{Doppler Frequency vs. Rotor Position with varying Elevation Angle}
		\label{fig:2D_theoretical_doppler}
	\end{center}
\end{figure}

@@

%formulate the geometric equations
\begin{equation}
	MaxDopplerProfile = f_{DopplerMax}cos(\theta_{Limited})
	\label{eq:theory_90_upper}
\end{equation}

@@

\begin{equation}
	MinDopplerProfile = -f_{DopplerMax}cos(\theta_{Limited})
	\label{eq:theory_90_lower}
\end{equation}

where $MaxDopplerProfile$ is an array of the maximum upper envelope values for each elevation sample, $MinDopplerProfile$ is an array of minimum lower envelope values for each elevation sample, and $\theta_{Limited}$ is the limited elevation angle range

\begin{equation}
	\theta_{Limited} = atan\left(\frac{Rx_z}{[0,\dots, (r_b - Rx_y)]}\right)
	\label{eq:theory_90_limited}
\end{equation}

where $Rx_z$ is the receivers position below the rotor head, $r_b$ is the length of the rotor blade, and $Rx_y$ is the receivers position on the Y axis.

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/background/3d_geometry_tx_90az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 90\textdegree}
		\label{fig:3D_model_90az_doppler}
	\end{center}
\end{figure}

@@

\begin{equation}
	\theta_{Limited} = atan\left(\frac{Rx_z}{[0, \dots, Rx_y]}\right)
	\label{eq:theory_270_limited}
\end{equation}

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/background/3d_geometry_tx_270az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 270\textdegree}
		\label{fig:3D_model_270az_doppler}
	\end{center}
\end{figure}

@@

%formulate the geometric equations
\begin{equation}
	MaxDopplerProfile = f_{DopplerMax}cos(\theta_{El})
	\label{eq:theory_180_upper}
\end{equation}

and the $MinDopplerProfile$ is set to 0 for the range.

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/background/3d_geometry_tx_180az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 180\textdegree}
		\label{fig:3D_model_180az_doppler}
	\end{center}
\end{figure}

Figure \ref{fig:3D_model_180az_doppler} shows the maximum and minimum Doppler profile values versus elevation angle for a transmitter at an azimuth angle of 180\textdegree. The data from the figure shows the maximum, of the Doppler profile, decrease as the elevation angle gets larger.

@@

%formulate the geometric equations
\begin{equation}
	MinDopplerProfile = -f_{DopplerMax}cos(\theta_{El})
	\label{eq:theory_0_lower}
\end{equation}

and the $MaxDopplerProfile$ is set to 0 for the range.

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/background/3d_geometry_tx_0az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 0\textdegree}
		\label{fig:3D_model_0az_doppler}
	\end{center}
\end{figure}

Figure \ref{fig:3D_model_0az_doppler} shows the maximum and minimum Doppler profile values versus elevation angle for a transmitter at an azimuth angle of 0\textdegree. The data from the figure shows the minimum of the Doppler profile increase as the elevation angle gets larger.

### 2016-10-24 MSc. Thesis Template.tex
starting edits for figures, got to end of azimuth sim

%% ----------------------------------------------------------------
\clearpage  %Start a new page
\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
\listofnomenclature{l p{5cm}| l}  % Include a list of Symbols (a three column table)
{
 \textbf{Symbol} & \textbf{Name} & \textbf{Units} \\
 $\theta_{El}$ & Transmitter Elevation angle & degrees \\
 $\theta_{r}$ & Ray Reflection angle & degrees \\
 $\theta_{Az}$ & Transmitter Azimuth angle & degrees \\
 $f_d$ & Doppler Frequency shift & Hz \\
 $\theta_b$ & Rotor Blade angle & degrees \\
 $Rx_x$ & Receiver position in X axis & meters \\
 $Rx_y$ & Receiver position in Y axis & meters \\
 $Rx_z$ & Receiver position in Z axis & meters \\
 $G_r$ & Receiver antenna gain & \\
 $G_t$ & Transmitter antenna gain& \\
 $R$ & Distance & meters\\
 $\vec{n}$ & Surface normal vector & \\
 $\vec{d_i}$ & Direction vector of incident ray & \\
 $\Gamma$ & Reflection loss coefficient & \\
 $\theta_i$ & Angle of incidence with an objects normal & radians \\
 $d$ & Total distance traveled by a ray & meters \\ 
 $t_0$ & Starting time in a frame & seconds \\
 $r$ & A radius along the length of the blade & meters \\
 $\omega_r$ & Rotational velocity of the blade & rad/second \\
 $F$ & Fading coefficient & \\
 $\lambda$ & Wavelength & meters \\
 $c$ & Speed of Light & meters/seconds \\
 $f$ & frequency & Hz \\
 $f_0$ & initial frequency & Hz \\
 $f_s$ & sampling frequency & samples/seconds \\
 $EnvelopeDifference$ & difference between two doppler envelopes & Hz \\
 $MaxUpperEnvelope$ & Array of values corresponding to the maximum of each azimuth or elevation upper envelope calculation & Hz \\
 $MinLowerEnvelope$ & Array of values corresponding to the minimum of each azimuth or elevation lower envelope calculation & Hz \\
 $BladeLength$ & Length of single rotor blade (radius of rotor) & meters \\
 $f_c$ & Center Frequency & Hz \\
 $R_{Estimate}$ & Estimated reflection radius & meters \\
 $f_{DopplerMax}$ & The maximum amount of doppler for a particular blade length and RPM & Hz \\
 $f_{DopplerCorrect}$ & The corrected doppler per $\theta_{Az}$ to be processed & Hz \\
 $A_{shift}$ & The amount of shift needed to correct for Blade pitch & Hz \\
}
%% ----------------------------------------------------------------
% End of the pre-able, contents and lists of things
% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
In RF communications with a rotorcraft such as a helicopter, the rotor blades can impart a modulation onto the received signal called Rotor Blade Modulation (RBM). This modulation is caused by the reflection of a signal off the rotating blades. The reflected signal is Doppler shifted based on where the signal is reflected along the length of the blade as well as the angle between the axis of rotation and the emitter. RBM is known to degrade the performance of RF communications on rotorcraft and can be used in radar applications to detect and classify aircraft, but there is little on its usefulness in other areas. This thesis looks at the ability to utilize the RBM phenomenon on the rotorcraft itself to geo-locate and track a signal emitter on the ground.

>>>>

%% ----------------------------------------------------------------
\clearpage  %Start a new page
\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
\listofnomenclature{l p{5cm}| l}  % Include a list of Symbols (a three column table)
{
 \textbf{Symbol} & \textbf{Name} & \textbf{Units} \\
 $\theta_{El}$ & Transmitter Elevation angle & degrees \\
 $\theta_{r}$ & Ray Reflection angle & degrees \\
 $\theta_{Az}$ & Transmitter Azimuth angle & degrees \\
 $f_d$ & Doppler Frequency shift & Hz \\
 $\theta_b$ & Rotor Blade angle & degrees \\
 $Rx_x$ & Receiver position in X axis & meters \\
 $Rx_y$ & Receiver position in Y axis & meters \\
 $Rx_z$ & Receiver position in Z axis & meters \\
 $G_r$ & Receiver antenna gain & \\
 $G_t$ & Transmitter antenna gain& \\
 $R$ & Distance & meters\\
 $\vec{n}$ & Surface normal vector & \\
 $\vec{d_i}$ & Direction vector of incident ray & \\
 $\Gamma$ & Reflection loss coefficient & \\
 $\theta_i$ & Angle of incidence with an objects normal & radians \\
 $r$ & A radius along the length of the blade & meters \\
 $\omega_r$ & Rotational velocity of the blade & rad/second \\
 $F$ & Fading coefficient & \\
 $\lambda$ & Wavelength & meters \\
 $c$ & Speed of Light & meters/seconds \\
 $f$ & frequency & Hz \\
 $f_0$ & initial frequency & Hz \\
 $f_s$ & sampling frequency & samples/seconds \\
 $ProfileDifference$ & Difference between two Doppler profiles & Hz \\
 $MaxDopplerProfile$ & Array of values corresponding to the maximum of each azimuth or elevation doppler profile calculation & Hz \\
 $MinDopplerProfile$ & Array of values corresponding to the minimum of each azimuth or elevation doppler profile calculation & Hz \\
 $r_b$ & Length of single rotor blade (radius of rotor) & meters \\
 $f_c$ & Center Frequency & Hz \\
 $R_{Estimate}$ & Estimated reflection radius & meters \\
 $f_{DopplerMax}$ & The maximum amount of doppler for a particular blade length and RPM & Hz \\
 $f_{DopplerCorrect}$ & The corrected doppler per $\theta_{Az}$ to be processed & Hz \\
 $A_{shift}$ & The amount of shift needed to correct for Blade pitch & Hz \\
}
%% ----------------------------------------------------------------
% End of the pre-able, contents and lists of things
% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
In RF communications with a rotorcraft such as a helicopter, the rotor blades can impart a modulation onto the received signal called Rotor Blade Modulation (RBM). This modulation is caused by the reflection of a signal off the rotating blades. The reflected signal is Doppler shifted based on where the signal is reflected along the length of the blade as well as the angle between the axis of rotation and the emitter. RBM is known to degrade the performance of RF communications on rotorcraft and can be used in radar applications to detect and classify aircraft, but there is little on its usefulness in other areas. This thesis looks at the ability to utilize the RBM phenomenon on the rotorcraft itself to geo-locate and track a signal emitter on the ground.

### 2016-10-24 Radio_Propagation_Simulation.tex
starting edits for figures, got to end of azimuth sim

\begin{equation}
	F = cos\left(2\pi \frac{d}{c} + t_0\right)
	\label{eqn:fading_coeff}
\end{equation}

where $F$ is the fading coefficient, $d$ is the total distance the particular ray has traveled, $c$ is the speed of light, and $t_0$ is the starting time of the current frame. The power can then be calculated using

\begin{equation}
	P_{faded} = PF
	\label{eqn:power_faded}
\end{equation}

where $P_{faded}$ is the adjusted power due to fading and $P$ is the signal power. The superposition of each ray's faded power becomes the received signal.

\subsection{Doppler Effect}
%define doppler effect
The Doppler effect is characterized by

%Doppler formula
\begin{equation}
	f = \left ( \frac{c + v_r}{c + v_s} \right ) f_0
	\label{eqn:formalDop}
\end{equation}

It is assumed that both the receiver and the transmitter are not moving therefore, the only Doppler imparted on the signal will be from the rotation of the blades. The associated Doppler is calculated using

@@

where $f_0$ is the initial transmitted frequency, $\lambda$ is the wavelength, $v_t$ is the velocity in the direction of the transmitter, and $v_r$ is the velocity in the direction of the reflection. This is similar to the Bistatic radar equation for Doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the Doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.

@@

>>>>

\textcolor{red}{FIGURE OUT WHAT TO PUT HERE FOR FADING COEFFICIENT?}

The power can then be calculated using

\textcolor{red}{FADING POWER?}

The superposition of each ray's faded power becomes the received signal.

\subsection{Doppler Effect}
%define doppler effect
It is assumed that both the receiver and the transmitter are not moving therefore, the only Doppler imparted on the signal will be from the rotation of the blades. The associated Doppler is calculated using

@@

where $f_0$ is the initial transmitted frequency, $\lambda$ is the wavelength, $v_t$ is the velocity in the direction of the transmitter, and $v_r$ is the velocity in the direction of the reflection. This is similar to the Bi-static radar equation for Doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the Doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.

@@

\textcolor{red}{ADD MORE ABOUT RAY TRACING}

### 2016-10-24 Simulation.tex
starting edits for figures, got to end of azimuth sim

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/test_analysis_spectrogram.eps}
		\caption{Example Spectrum for one Blade revolution with transmitter at Azimuth of 45\textdegree \space and Elevation of 35\textdegree}
		\label{fig:test_spec}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/test_analysis_spectrogram_with_envelope.eps}
		\caption{Example Spectrum with Doppler Profile for one Blade revolution with transmitter at Azimuth of 45\textdegree \space and Elevation of 35\textdegree}
		\label{fig:test_spec_w_doppler_profile}
	\end{center}
\end{figure}

@@

%figure of doppler vs azimuth angle
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_200_max_doppler.eps}
		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 45\textdegree}
		\label{fig:tx_azimuth_angle_200}
	\end{center}
\end{figure}
%azimuth variable, elevation = 45deg

@@

%figure of doppler and azimuth angle for different elevation angles.
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_50_max_doppler.eps}
		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 76\textdegree}
		\label{fig:tx_azimuth_angle_50}
	\end{center}
\end{figure}
%azimuth variable, elevation = 76deg

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_400_max_doppler.eps}
		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 26.5\textdegree}
		\label{fig:tx_azimuth_angle_400}
	\end{center}
\end{figure}
%azimuth variable, elevation = 26.5deg

>>>>

\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/simulation/test_analysis_spectrogram.eps}
		\caption{Example Spectrum for one Blade revolution with transmitter at Azimuth of 45\textdegree \space and Elevation of 35\textdegree}
		\label{fig:test_spec}
	\end{center}
\end{figure}

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/simulation/test_analysis_spectrogram_with_envelope.eps}
		\caption{Example Spectrum with Doppler Profile for one Blade revolution with transmitter at Azimuth of 45\textdegree \space and Elevation of 35\textdegree}
		\label{fig:test_spec_w_doppler_profile}
	\end{center}
\end{figure}

@@

%figure of doppler vs azimuth angle
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_200_max_doppler.eps}
		\caption{Max and Min Doppler Profile Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 45\textdegree}
		\label{fig:tx_azimuth_angle_200}
	\end{center}
\end{figure}
%azimuth variable, elevation = 45deg

@@

%figure of doppler and azimuth angle for different elevation angles.
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_50_max_doppler.eps}
		\caption{Max and Min Doppler Profile Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 76\textdegree}
		\label{fig:tx_azimuth_angle_50}
	\end{center}
\end{figure}
%azimuth variable, elevation = 76deg

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_400_max_doppler.eps}
		\caption{Max and Min Doppler Profile Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 26.5\textdegree}
		\label{fig:tx_azimuth_angle_400}
	\end{center}
\end{figure}
%azimuth variable, elevation = 26.5deg
